Synthesizing Symmetric Lenses

### 2018-07-10 papers/SymmetricLenses/main.tex
eval changes

To compare to the existing bijective synthesis algorithm, we run our symmetric
synthesis algorithm on the original Optician benchmark suite. \afm{8} of these
benchmarks had to be slightly altered with tighter specifications or termination
parameters\dpw{What does that mean? You had to alter it to get the system to work?}, as we had to alter the original specifications to generate the
correct lens.

@@

\subsection{The Effects of Our Heuristics}
\label{subsec:effect-of-heuristics}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \AnyOpt{}: & We synthesize any lens \dpw{Did you mean the following? But is the order truly arbitrary? Is size or anything else a driver?:] We synthesize lenses in an arbitrary order (i.e. without use of the information theoretic preference metric)} that satisfies the specification, with no
               notion of cost.\\
  \FLOpt{}: &  The first time \GreedySynth finds a lens, the synthesis procedure
              returns that lens.\dpw{What controls the ``greediness''? Say a little something else to more clearly differentiate from Any.}\\
  \CCOpt{}: & We replace our information theoretic cost metric with one where
              the cost of the lens is the number of disonnects plus the number
              of merges.\\
  \ZTOpt{}: & \ZTOpt{} runs the algorithm with the termination parameter
    universally set to 0 (default). \\
  \TFTOpt{}: & \TFTOpt{} runs the algorithm with the
    termination parameter universally set to 25. \\
  \NTFTOpt{}: & \NTFTOpt{} runs the algorithm with the
    termination parameter universally set to -25. \\
\end{tabulary}

>>>>

To compare to the existing bijective synthesis algorithm, we run our symmetric
synthesis algorithm on the original Optician benchmark suite. \afm{8} of these
benchmarks had to be slightly altered to work with our new system. We altered
these benchmarks by either providing additional examples termination parameters.
Without these alterations, the symmetric synthesis synthesized a lens that fit
the specification but not the intended lens.

@@

\subsection{The Effects of Our Heuristics}
\label{subsec:effect-of-heuristics}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \AnyOpt{}: & We synthesize lenses without use of the information
               theoretic preference metric.  Once \GreedySynth finds a lens, the
  synthesis procedure returns that lens.\\
  \FLOpt{}: &  The first time \GreedySynth finds a lens, the synthesis procedure
              returns that lens. However, \GreedySynth uses the information
              theoretic preference metric to choose a lens.\\
  \CCOpt{}: & We replace our information theoretic cost metric with one where
              the cost of the lens is the number of disonnects plus the number
              of merges.\\
  \ZTOpt{}: & \ZTOpt{} runs the algorithm with the termination parameter
              universally set to 0 (default). \\
  \TFTOpt{}: & \TFTOpt{} runs the algorithm with the
               termination parameter universally set to 25. \\
  \NTFTOpt{}: & \NTFTOpt{} runs the algorithm with the
                termination parameter universally set to -25. \\
\end{tabulary}
